\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 lang-design.tex
spacing

\begin{centered}
\begin{minipage}{.71\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_rect : \forall (P : tm -> Type), [@\hlcase{tm-recursor-case-unit}@]P tm_unit[@\tikzmarkend{tm-recursor-case-unit}@] -> [@\hlcase{tm-recursor-case-var}@](\forall x, P (tm_var x))[@\tikzmarkend{tm-recursor-case-var}@] ->
         [@\hlcase{tm-recursor-case-abs}@](\forall x t, P t -> P (tm_abs x t))[@\tikzmarkend{tm-recursor-case-abs}@] ->
         [@\hlcase{tm-recursor-case-app}@](\forall t1, P t1 -> \forall t2, P t2 -> P (tm_app t1 t2))[@\tikzmarkend{tm-recursor-case-app}@] -> \forall t, P t
\end{lstlisting}
\end{minipage}
\end{centered}

@@

\begin{centered}
\begin{minipage}{.97\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_prect_STLC : \forall (P : tm -> Type), [@\hlcase{tm-partialrec-case-unit}@]option (P tm_unit)[@\tikzmarkend{tm-partialrec-case-unit}@] -> [@\hlcase{tm-partialrec-case-var}@](\forall x, option (P (tm_var x)))[@\tikzmarkend{tm-partialrec-case-var}@] ->
                [@\hlcase{tm-partialrec-case-abs}@](\forall x t, option (P t) -> option (P (tm_abs x t)))[@\tikzmarkend{tm-partialrec-case-abs}@] ->
                [@\hlcase{tm-partialrec-case-app}@](\forall t1, option (P t1) -> \forall t2, option (P t2) -> option (P (tm_app t1 t2)))[@\tikzmarkend{tm-partialrec-case-app}@] ->
                \forall t, option (P t)
\end{lstlisting}
\end{minipage}
\end{centered}

>>>>

\begin{centered}
\begin{minipage}{.71\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9.9}\ttfamily]
tm_rect : \forall (P : tm -> Type), [@\hlcase{tm-recursor-case-unit}@]P tm_unit[@\tikzmarkend{tm-recursor-case-unit}@] -> [@\hlcase{tm-recursor-case-var}@](\forall x, P (tm_var x))[@\tikzmarkend{tm-recursor-case-var}@] ->
         [@\hlcase{tm-recursor-case-abs}@](\forall x t, P t -> P (tm_abs x t))[@\tikzmarkend{tm-recursor-case-abs}@] ->
         [@\hlcase{tm-recursor-case-app}@](\forall t1, P t1 -> \forall t2, P t2 -> P (tm_app t1 t2))[@\tikzmarkend{tm-recursor-case-app}@] -> \forall t, P t
\end{lstlisting}
\end{minipage}
\end{centered}

@@

\begin{centered}
\begin{minipage}{\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9.9}\ttfamily]
tm_prect_STLC : \forall (P : tm -> Type), [@\hlcase{tm-partialrec-case-unit}@]option (P tm_unit)[@\tikzmarkend{tm-partialrec-case-unit}@] -> [@\hlcase{tm-partialrec-case-var}@](\forall x, option (P (tm_var x)))[@\tikzmarkend{tm-partialrec-case-var}@] ->
  [@\hlcase{tm-partialrec-case-abs}@](\forall x t, option (P t) -> option (P (tm_abs x t)))[@\tikzmarkend{tm-partialrec-case-abs}@] ->
  [@\hlcase{tm-partialrec-case-app}@](\forall t1, option (P t1) -> \forall t2, option (P t2) -> option (P (tm_app t1 t2)))[@\tikzmarkend{tm-partialrec-case-app}@] -> \forall t, option (P t)
\end{lstlisting}
\end{minipage}
\end{centered}

%\begin{centered}
%\begin{minipage}{.97\textwidth}
%\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
%\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
%tm_prect_STLC : \forall (P : tm -> Type), [@\hlcase{tm-partialrec-case-unit}@]option (P tm_unit)[@\tikzmarkend{tm-partialrec-case-unit}@] -> [@\hlcase{tm-partialrec-case-var}@](\forall x, option (P (tm_var x)))[@\tikzmarkend{tm-partialrec-case-var}@] ->
%                [@\hlcase{tm-partialrec-case-abs}@](\forall x t, option (P t) -> option (P (tm_abs x t)))[@\tikzmarkend{tm-partialrec-case-abs}@] ->
%                [@\hlcase{tm-partialrec-case-app}@](\forall t1, option (P t1) -> \forall t2, option (P t2) -> option (P (tm_app t1 t2)))[@\tikzmarkend{tm-partialrec-case-app}@] ->
%                \forall t, option (P t)
%\end{lstlisting}
%\end{minipage}
%\end{centered}
